---
title: "ADHD Report"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
```

## Logistic Regression using SWAG

The plot shows the range of CV errors for each dimension. There is a clear decay in CV errors as the dimension increases.

```{r}
library(png)
img1_path <- "images/CV-plot-LogReg.png"
img1 <- readPNG(img1_path, native = TRUE)
```


\begin{table}
\centering
\begin{tabular}[t]{||c|c|c||}
\hline
Feature & Variable & Frequency \\
\hline \hline
'Insula-R' $\leftrightarrow$ 'Paracentral-Lobule-R' & 54.21 &	381 \\
\hline
'Frontal-Sup-R'$\leftrightarrow$ 'Frontal-Mid-R' & 72.68 & 381 \\
\hline
'Temporal-Mid-L'$\leftrightarrow$ 'Lingual-L'& 101.85 &	381\\
\hline
'Insula-L'$\leftrightarrow$ 'Frontal-Mid-L' & 116.89 & 381\\
\hline
'Frontal-Sup-R'$\leftrightarrow$ 'Frontal-Inf-Orb-R' & 104.34 & 377\\
\hline
'Supp-Motor-Area-L'$\leftrightarrow$ 'SupraMarginal-L' & 151.147 & 377\\
\hline
Frontal-Sup-R'$\leftrightarrow$ 'ParahippocampaGyrus' & 72.11 &	363\\
\hline
'Vermis-1-2'$\leftrightarrow$ 'Temporal-Mid-L' & 150.114 & 363\\
\hline
'Vermis-4-5'$\leftrightarrow$ 'Frontal-Sup-Orb-R' & 126.2	& 325\\
\hline
'Frontal-Sup-Medial-L'$\leftrightarrow$ 'Cingulum-Mid-L'& 124.99 & 284\\
\hline
'Temporal-Mid-L'$\leftrightarrow$ 'Pallidum-R'& 114.40 & 281\\
\hline
'Occipital-Mid-L'$\leftrightarrow$ 'Cerebelum-Crus2-L' & 162.73 & 267\\
\hline
'Cingulum-Ant-L'$\leftrightarrow$ Paracentral-Lobule-R' & 47.21	& 258\\
\hline
'Temporal-Pole-Sup-R'$\leftrightarrow$ 'Frontal-Mid-L' & 146.89 & 235\\
\hline
'Frontal-Mid-L'$\leftrightarrow$ 'Caudate-R' & 108.27 & 207\\
\hline
'Frontal-Mid-L'$\leftrightarrow$ 'Frontal-Sup-L' & 108.91 & 201\\
\hline
'Temporal-Mid-L'$\leftrightarrow$ 'Temporal-Sup-L' & 114.28 & 172\\
\hline
'Frontal-Sup-R'$\leftrightarrow$ 'Precuneus-R' & 173.9 & 149\\
\hline
'Insula-L'$\leftrightarrow$ 'Postcentral-R' & 116.55 & 84\\
\hline
'Frontal-Mid-L'$\leftrightarrow$ 'Cingulum-Ant-L' & 108.47 & 73\\
\hline
'Frontal-Sup-Medial-R'$\leftrightarrow$ 'Cingulum-Mid-L' & 134.99	& 66\\
\hline
'Cingulum-Post-L'$\leftrightarrow$ 'Postcentral-R' & 74.55 & 63\\
\hline
'Supp-Motor-Area-L'$\leftrightarrow$ 'SupraMarginal-L'& 151.46 & 55\\
\hline
'Frontal-Sup-L'$\leftrightarrow$ 'ParahippocampaGyrus' & 13.11 & 51\\
\hline
'Caudate-R'$\leftrightarrow$ 'Paracentral-Lobule-R'& 27.21	& 51\\
\hline
'Frontal-Sup-Medial-R'$\leftrightarrow$ 'Frontal-Inf-Tri-L'& 134.23 & 46\\
\hline
'Insula-L'$\leftrightarrow$ 'Paracentral-Lobule-R'& 116.21 &	45\\
\hline
'Cingulum-Post-L'$\leftrightarrow$ 'Paracentral-Lobule-R'& 74.21 &	43\\
\hline
'Parietal-Sup-R'$\leftrightarrow$ 'Cuneus-L'& 184.58 & 37\\
\hline
'Cingulum-Ant-R'$\leftrightarrow$ 'Frontal-Sup-R'& 189.173 &	37\\
\hline
'Parietal-Inf-L'$\leftrightarrow$ 'Caudate-Head-L'& 169.49 &	34\\
\hline
'Frontal-Sup-Medial-L'$\leftrightarrow$ 'Frontal-Inf-Tri-L'& 124.23 &	28\\
\hline
'Insula-R'$\leftrightarrow$ 'Pallidum-R'& 129.40 & 25\\
\hline
'Temporal-Mid-L'$\leftrightarrow$ 'Putamen-L'& 114.6 & 23\\
\hline
'Insula-L'$\leftrightarrow$ 'Cingulum-Ant-L'& 116.47 & 23\\
\hline
'Caudate-Head-L'$\leftrightarrow$ 'Cingulum-Ant-L'& 49.47 & 21\\
\hline
'Frontal-Med-Or-R'$\leftrightarrow$ 'Frontal-Inf-Tri-L'& 138.23 &	20\\
\hline
'Vermis-4-5'$\leftrightarrow$ 'Frontal-Sup-Medial-L'& 126.124 &	18\\
\hline
'Frontal-Sup-R'$\leftrightarrow$ 'Cingulum-Ant-L'& 173.47 &	13\\
\hline
'Cingulum-Mid-R'$\leftrightarrow$ 'Frontal-Sup-L'& 82.13 &	12\\
\hline
'Frontal-Med-Orb-R'$\leftrightarrow$ 'Frontal-Mid-R'& 138.107 &	9\\
\hline
'Rolandic-Oper-L'$\leftrightarrow$ 'Temporal-Inf-L'& 148.71 &	9\\
\hline
'Lingual-L'$\leftrightarrow$ 'Frontal-Sup-L'& 85.13 &	8\\
\hline
'Cingulum-Ant-R'$\leftrightarrow$ 'Frontal-Mid-L'& 112.67	& 7\\
\hline
'Cingulum-Ant-R'$\leftrightarrow$ 'Cingulum-Mid-L'& 189.65 &	7\\
\hline
'Cingulum-Ant-L'$\leftrightarrow$ 'Precuneu-R'& 47.9 &	5\\
\hline
'Pallidum-R'$\leftrightarrow$ 'Temporal-Mid-R'& 40.19 &	3\\
\hline
'Caudate-Head-L'$\leftrightarrow$ 'Precuneus-R'& 49.9 &	3\\
\hline
'Cingulum-Ant-L'$\leftrightarrow$ 'Caudate-R'& 47.27 &	1\\
\hline
'Temporal-Inf-L'$\leftrightarrow$ 'Lingual-L'& 132.85	& 1\\
\hline
'Temporal-Sup-L'$\leftrightarrow$ 'Temporal-Mid-L'& 135.114 &	1\\
\hline
'Vermis-6'$\leftrightarrow$ 'Temporal-Inf-L'& 136.132 &	1\\
\hline
'Cingulum-Ant-R'$\leftrightarrow$ 'Paracentral-Lobule-R'& 189.21 & 1\\
\hline
\end{tabular}
\end{table}

There are a total of 381 models of dimensions 9 to 20. The table below shows the frequency of each feature selected. The most frequent features are 'Insula-R' \(\leftrightarrow\) 'Paracentral-Lobule-R', 'Frontal-Sup-R' \(\leftrightarrow\) 'Frontal-Mid-R', 'Temporal-Mid-L' \(\leftrightarrow\) 'Lingual-L' and 'Insula-L' \(\leftrightarrow\) 'Frontal-Mid-L',  which are contained by every model.

\newpage

## SVM Linear Analysis using SWAG

The plot shows the range of CV errors for each dimension.

```{r}
library(png)
img2_path <- "images/CV-plot-SVML.png"
img2 <- readPNG(img2_path, native = TRUE)
```

## FREQUENCY TABLE

In the post-processing, we took the minimum CV_alpha and selected all the models who have CV_alpha less than or equal to it. The minimum CV_alpha is 0.220925 and is the CV of dimension 20.

There are a total of 114 models of dimensions 18, 19, 20. "54,21", "91,85", "105,10", "121,68", "126,2", "135,105", "140,53", "150,114", "152,22", "154,112", "174,73" features are present in all the models. Below is the frequency table.

\begin{table}
\begin{tabular}[t]{||c|c|c||}
\hline
Feature & Variable & Frequency \\
\hline \hline
'Insula-R'$\leftrightarrow$ 'Paracentral-Lobule-R'& 54.21 &	114 \\
\hline
'Frontal-Sup-L'$\leftrightarrow$ 'Lingual-L' & 91.85 & 114 \\
\hline
'Thalamus-L'$\leftrightarrow$ 'Frontal-Sup-Medial-L' & 105.10 & 114\\
\hline
'Olfactory'$\leftrightarrow$ 'Frontal-Mid-R' & 121.68 &	114\\
\hline
'Vermis-4-5'$\leftrightarrow$ 'Frontal-Sup-Orb-R' & 126.2 &	114\\
\hline
'Temporal-Sup-L'$\leftrightarrow$ 'Thalamus-L' & 135.105 &	114\\
\hline
'Parietal-Inf-R'$\leftrightarrow$ 'Precentral-R' & 140.53 &	114\\
\hline
'Vermis-1-2'$\leftrightarrow$ 'Temporal-Mid-L'& 150.114	& 114\\
\hline
'Angular-R'$\leftrightarrow$ 'Fusiform-L'& 152.22 & 114\\
\hline
'Fusiform-R'$\leftrightarrow$ 'Cingulum-Ant-R' & 154.112	& 114\\
\hline
'Cerebelum-6-L'$\leftrightarrow$ 'Cerebelum-Crus2-L' & 174.73	& 114\\
\hline
'Parietal-Inf-L'$\leftrightarrow$ 'Temporal-Pole-Mid-L'& 183.12	& 106\\
\hline
'Thalamus-L'$\leftrightarrow$'Frontal-Sup-L' & 105.91	& 71\\
\hline
'Vermis-1-2'$\leftrightarrow$'Pallidum-R' & 150.40	& 67\\
\hline
'Cuneus-R'$\leftrightarrow$'Frontal-Inf-Orb-L' & 70.14	& 66\\
\hline
'Frontal-Sup-Medial-L'$\leftrightarrow$'Precentral-L' & 130.80	& 66\\
\hline
'Frontal-Mid-R'$\leftrightarrow$'Cingulum-Ant-L' & 161.47 & 66\\
\hline
'Parietal-Inf-L'$\leftrightarrow$'Fusiform-R' & 157.81	& 56\\
\hline
'Frontal-Sup-Orb-L'$\leftrightarrow$'Cuneus-L' & 78.58	& 40\\
\hline
'Angular-R'$\leftrightarrow$'Cerebelum-Crus2-L' & 92.73	& 39\\
\hline
'Rolandic-Oper-L'$\leftrightarrow$'Frontal-Inf-Orb-L' & 148.14	& 28\\
\hline
'Midbrain'$\leftrightarrow$'Temporal-Sup-L' & 165.135 & 27\\
\hline
'Temporal-Pole-Sup-R'$\leftrightarrow$'Frontal-Inf-Orb-R' & 185.34	& 24\\
\hline
'Cingulum-Ant-R'$\leftrightarrow$'Temporal-Mid-R' & 189.8	& 22\\
\hline
'SupraMarginal-L'$\leftrightarrow$'Cingulum-Mid-L' & 147.65	& 16\\
\hline
'Parietal-Inf-L'$\leftrightarrow$'Cingulum-Ant-L' & 169.47 & 15\\
\hline
'Frontal-Sup-R'$\leftrightarrow$'Putamen-L' & 72.6 & 12\\
\hline
'Precentral-L'$\leftrightarrow$'Occipital-Mid-R'& 80.77 & 12\\
\hline
'Temporal-Mid-L'$\leftrightarrow$'Frontal-Inf-Orb-L' & 187.14 & 11\\
\hline
'Parietal-Inf-L'$\leftrightarrow$'Precuneus-L' & 169.18 & 10\\
\hline
'Frontal-Inf-Oper-R'$\leftrightarrow$'SupraMarginal-R' & 190.127 & 10\\
\hline
'Occipital-Mid-R'$\leftrightarrow$'Lingual-R' & 77.4 & 9\\
\hline
'Occipital-Sup-R'$\leftrightarrow$'Parietal-Sup-R' & 137.131 &	9\\
\hline
'Thalamus-R'$\leftrightarrow$'Frontal-Sup-Medial-L' & 62.10 & 8\\
\hline
'Temporal-Mid-L'$\leftrightarrow$'Frontal-Mid-R & 114.68 & 8\\
\hline
'Frontal-Mid-L'$\leftrightarrow$'Frontal-Sup-L' & 79.13 & 7\\
\hline
'Cingulum-Ant-R'$\leftrightarrow$'Frontal-Inf-Orb-R' & 189.34 & 7\\
\hline
'Insula-L'$\leftrightarrow$'Brainstem' & 61.35 &	6\\
\hline
'Calcarine-L'$\leftrightarrow$'Cerebelum-8-R' & 88.45 &	6\\
\hline
'Frontal-Med-Orb-R'$\leftrightarrow$'Frontal-Mid-L'& 138.89 & 6\\
\hline
'Rolandic-Oper-L'$\leftrightarrow$'Temporal-Pole-Sup-R'& 148.146 & 6\\
\hline
'Frontal-Inf-Orb-L'$\leftrightarrow$'Putamen-L'& 14.6 & 5\\
\hline
'Cingulum-Mid-R'$\leftrightarrow$'Frontal-Mid-L' & 82.69	& 5\\
\hline
'Temporal-Pole-Sup-R'$\leftrightarrow$'Supp-Motor-Area-R' & 146.30 &	5\\
\hline
'Cerebelum-8-R'$\leftrightarrow$'Cerebelum-6-L' & 155.7 & 5\\
\hline
'Rectus-L'$\leftrightarrow$'Brainstem' & 188.35 & 5\\
\hline
'Rectus-L'$\leftrightarrow$'Cingulum-Mid-L' & 188.99 & 5\\
\hline
'Rectus-L'$\leftrightarrow$'Cerebelum-6-L' & 188.174 & 5\\
\hline
'Cingulum-Ant-R'$\leftrightarrow$'Temporal-Mid-R' & 189.64 & 5\\
\hline
'Frontal-Inf-Oper-R'$\leftrightarrow$'Frontal-Inf-Tri-R' & 190.3 &	5\\
\hline
'Cuneus-L'$\leftrightarrow$'Precuneus-L' & 58.38 & 4\\
\hline
'Thalamus-L'$\leftrightarrow$'Frontal-Sup-Medial-R' & 105.83 & 4\\
\hline
'Frontal-Mid-L'$\leftrightarrow$'Frontal-Sup-Medial-L' & 108.10 & 4\\
\hline
\end{tabular}
\end{table}


\begin{table}
\begin{tabular}[t]{||c|c|c||}
\hline
Feature & Variable & Frequency \\
\hline \hline
'Occipital-Sup-R'$\leftrightarrow$'Precuneus-R' & 137.9 &	4\\
\hline
'Frontal-Inf-Oper-R'$\leftrightarrow$'Cingulum-Mid-R' & 164.82 & 4\\
\hline
'Midbrain'$\leftrightarrow$'Frontal-Inf-Tri-L' & 165.23 & 4\\
\hline
'Cerebelum-6-L'$\leftrightarrow$'Temporal-Inf-R' & 174.57 & 4\\
\hline
'Frontal-Sup-R'$\leftrightarrow$'Frontal-Mid-Orb-R'& 104.90 & 3\\
\hline
'Insula-L'$\leftrightarrow$'Supp-Motor-Area-R' & 116.30 & 3\\
\hline
'Insula-L'$\leftrightarrow$'Postcentral-R' & 116.42 & 3\\
\hline
'Caudate-R'$\leftrightarrow$'Temporal-Pole-Mid-R' & 117.102 & 3\\
\hline
'Precentral-L'$\leftrightarrow$'Insula-L' & 128.116 & 3\\
\hline
'Temporal-Sup-L'$\leftrightarrow$'Cingulum-Mid-R' & 135.82 & 3\\
\hline
'Supp-Motor-Area-L'$\leftrightarrow$'Angular-L' & 139.118 & 3\\
\hline
'Precuneus-L'$\leftrightarrow$'Precuneus-L' & 145.18 &	3\\
\hline
'RectalGyrus'$\leftrightarrow$'Frontal-Inf-Orb-R' & 168.34 & 3\\
\hline
'Cuneus-L'$\leftrightarrow$'Cingulum-Ant-L' & 58.47 &	2\\
\hline
'Occipital-Mid-R'$\leftrightarrow$'Temporal-Mid-R' & 77.19 &	2\\
\hline
'Frontal-Sup-Medial-R'$\leftrightarrow$'Caudate-R' & 83.27 & 2\\
\hline
'Angular-R'$\leftrightarrow$'Frontal-Sup-Orb-R' & 92.2 & 2\\
\hline
'Supp-Motor-Area-L'$\leftrightarrow$'SupraMarginal-L' & 151.147	& 2\\
\hline
'RectalGyrus'$\leftrightarrow$'Cerebelum-8-R' & 168.97 & 2\\
\hline
'Paracentral-Lobule-L'$\leftrightarrow$'Postcentral-R' & 177.55 & 2\\
\hline
'Paracentral-Lobule-L'$\leftrightarrow$'Cingulum-Mid-L' & 177.65 & 2\\
\hline
'Temporal-Mid-L'$\leftrightarrow$'Cingulum-Ant-L' & 179.47 & 2\\
\hline
'Parietal-Inf-L'$\leftrightarrow$'Angular-L' & 183.118 & 2\\
\hline
'Cingulum-Ant-R'$\leftrightarrow$'Cingulum-Mid-L' & 189.99 & 2\\
\hline
'Cuneus-L'$\leftrightarrow$Putamen-L' & 24.6 & 1\\
\hline
'Insula-L'$\leftrightarrow$'Temporal-Mid-L' & 61.31 &	1\\
\hline
'Frontal-Mid-L'$\leftrightarrow$'Temporal-Inf-R'& 69.15 & 1\\
\hline
'Cingulum-Mid-R'$\leftrightarrow$'Precentral-L' & 82.80 & 1\\
\hline
'Parietal-Sup-L'$\leftrightarrow$'Precentral-R' & 95.53 &	1\\
\hline
'Cingulum-Mid-L'$\leftrightarrow$'Frontal-Inf-Orb-L' & 99.14 & 1\\
\hline
'Temporal-Inf-L'$\leftrightarrow$'Frontal-Sup-L' & 103.91 & 1\\
\hline
'Frontal-Sup-R'$\leftrightarrow$'Paracentral-Lobule-R'& 104.21 & 1\\
\hline
'Vermis-9'$\leftrightarrow$'Frontal-Mid-R' & 113.107 & 1\\
\hline
'Temporal-Mid-L'$\leftrightarrow$'Frontal-Sup-R' & 114.72 &	1\\
\hline
'Postcentral-R'$\leftrightarrow$'Insula-R' & 115.54 & 1\\
\hline
'Insula-L'$\leftrightarrow$'Parietal-Sup-L' & 116.95 & 1\\
\hline
'Frontal-Mid-Orb-L'$\leftrightarrow$'Cingulum-Mid-L' & 119.99 & 1\\
\hline
'Frontal-Sup-Medial-L'$\leftrightarrow$'Frontal-Inf-Orb-R' & 124.34 & 1\\
\hline
'Temporal-Sup-L'$\leftrightarrow$'Postcentral-R' & 135.55 & 1\\
\hline
'Frontal-Med-Orb-R'$\leftrightarrow$'Angular-R' & 138.92 & 1\\
\hline
'Supp-Motor-Area-L'$\leftrightarrow$'Frontal-Mid-R'& 139.20 & 1\\
\hline
'Temporal-Pole-Sup-R'$\leftrightarrow$'Temporal-Mid-L' & 146.31 & 1\\
\hline
'Temporal-Pole-Sup-R'$\leftrightarrow$'Frontal-Sup-Orb-L' & 146.78 &	1\\
\hline
'SupraMarginal-L'$\leftrightarrow$'Frontal-Mid-Orb-L' & 147.33 & 1\\
\hline
'Rolandic-Oper-L'$\leftrightarrow$'Cingulum-Ant-L' & 148.47 & 1\\
\hline
'Rolandic-Oper-L'$\leftrightarrow$'Frontal-Mid-L' &148.89 & 1\\
\hline
'Cerebelum-3-R'$\leftrightarrow$'Thalamus-R' & 160.62 & 1\\
\hline
'Postcentral-L'$\leftrightarrow$'Postcentral-R' & 163.55 & 1\\
\hline
'Precentral-L'$\leftrightarrow$'Cingulum-Ant-R' & 166.112 & 1\\
\hline
'RectalGyrus'$\leftrightarrow$'Insula-L' & 168.116 &	1\\
\hline
'Parietal-Inf-L'$\leftrightarrow$'Frontal-Mid-L' & 169.108	& 1\\
\hline
'Occipital-Sup-L'$\leftrightarrow$'Occipital-Mid-R' & 171.59 & 1\\
\hline
'Frontal-Inf-Orb-R'$\leftrightarrow$'Vermis-6' & 172.136 & 1\\
\hline
'Fusiform-R'$\leftrightarrow$'Caudate-R' & 175.27 & 1\\
\hline
'Parietal-Inf-L'$\leftrightarrow$'Paracentral-Lobule-R' & 183.21 & 1\\
\hline
'Temporal-Pole-Sup-R'$\leftrightarrow$'Thalamus-R' & 185.62 &	1\\
\hline
'Temporal-Mid-L'$\leftrightarrow$'Temporal-Inf-L' & 187.60 &	1\\
\hline
\end{tabular}
\end{table}

