---
title: "SWAG using Logistic Regression"
output: html_document
date: '2023-01-30'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Logistic Regression Using SWAG

```{r message=FALSE, warning=FALSE}
## Loading the train dataset
DATA <-  read.csv("train_data.csv")
adhd0 <- t(DATA)
adhd1 <- adhd0[-1, ]

#naming the colnames
colnames(adhd1) <- as.character(adhd1[1, ])
X <- apply(adhd1[,-1],2, as.numeric)
X <- data.frame(adhd1[ ,1],X)
adhd2 <- X[-1, ]
adhd3 <- as.matrix(adhd2)
colnames(adhd3)[1] <- "GROUP"

#defining control group=0  
cat_v <- c()
for (i in 1:dim(adhd3)[1]){
  if(adhd3[ ,"GROUP"][i] == "Controls")
  {
    cat_v[i]<-"0"
  }else{
    cat_v[i]<-"1"
  }
}
#as.factor(cat_v)
adhd3 <- data.frame(cat_v, adhd3)
Z <- adhd3[ ,-2]
Z <- apply(Z,2,as.numeric)
r <- Z[ ,1]
r <- as.matrix(r)
adhd <- Z[ ,-1]

rm(list=c("adhd0", "adhd1", "adhd2", "adhd3", "Z"))
```



```{r message=FALSE, warning=FALSE}
## Splitting the training dataset

#training and testing data
## % 80 of the sample size
ind <- floor(0.8 * nrow(adhd))
set.seed(2705)
train_ind <- sample(seq_len(nrow(adhd)), size = ind)

x_train <- as.data.frame(adhd[train_ind, ])
y_train <- as.factor(r[train_ind, ])
x_test <- as.data.frame(adhd[-train_ind, ])
y_test <- as.factor(r[-train_ind, ])
```


```{r message=FALSE, warning=FALSE}
## Loading the Original test dataset

#test dataset

DATA1 <-  read.csv("test_data.csv")
ADHD0 <- t(DATA1)
ADHD1 <- ADHD0[-1, ]

#naming the colnames
colnames(ADHD1) <- as.character(ADHD1[1, ])
X_t <- apply(ADHD1[,-1],2, as.numeric)
X_t <- data.frame(ADHD1[ ,1],X_t)
ADHD2 <- X_t[-1, ]
ADHD3 <- as.matrix(ADHD2)
colnames(ADHD3)[1] <- "group"

#defining control group=0  
cat_t <- c()
for (i in 1:dim(ADHD3)[1]){
  if(ADHD3[ ,"group"][i] == "Controls")
  {
    cat_t[i]<-"0"
  }else{
    cat_t[i]<-"1"
  }
}
ADHD3 <- data.frame(cat_t, ADHD3)
Y<- ADHD3[ ,-2]
Y <- apply(Y,2,as.numeric)
colnames(Y)[1] <- "Group_t"

rm(list=c("ADHD0", "ADHD1", "ADHD2", "ADHD3"))
```



```{r message=FALSE, warning=FALSE}
## Loading the SWAG Logistic Regression results
load("Logistic_Regression_Results.Rda")
```


```{r message=FALSE, warning=FALSE}
library("writexl")
## Post-processing
min_error = min(train_swag_svml$cv_alpha)


varmat_ind = list() #saves the varmat index from CV errors
for(i in 1:20){
  varmat_ind[[i]]=which(train_swag_svml$CVs[[i]]<=min_error, arr.ind = T)
}

post_sel = list() # models selected after post-processing
for(i in 1:20){
  post_sel[[i]] = train_swag_svml$VarMat[[i]][,varmat_ind[[i]]]
}

post_sel[[1]] = t(as.matrix(post_sel[[1]]))

for(i in 1:20){
  if(!is.matrix(post_sel[[i]])){
    post_sel[[i]]=t(as.matrix(post_sel[[i]]))
  }
}

post_sel[[9]] = t(post_sel[[9]])


x = c() #non-empty elements of post-group
for(i in 1:20){
  if(length(post_sel[[i]])!=0){
    x = c(x,i)
  }
  x = x
}

for(i in 1:length(x)){
  if(nrow(post_sel[[x[i]]])<20){
    diff = 20 - nrow(post_sel[[x[i]]])
    post_sel[[x[i]]] = rbind(post_sel[[x[i]]],matrix(NA,nrow = diff, ncol = ncol(post_sel[[x[i]]])))
  } 
}


models = matrix(NA, nrow = 20,ncol=ncol(post_sel[[x[1]]]))

models[1:nrow(post_sel[[x[1]]]),]=post_sel[[x[1]]]

for(i in 2:length(x)){
  models = cbind(models,post_sel[[x[i]]])
}

models = t(models)

selected_var = c() 
for(i in 1:ncol(models)){
  selected_var = c(selected_var,models[,i])
}
selected_var = na.omit(unique(selected_var))
selected_var = sort(selected_var)
#colnames(x_train)[selected_var]
#table(models)

freq = table(models)
variable = colnames(x_train)[selected_var]

freq_table = cbind(variable,freq)
rownames(freq_table) = c(1:nrow(freq_table))
freq_table = as.data.frame(freq_table)
freq_table$freq = as.numeric(freq_table$freq)
as.data.frame(freq_table)
write_xlsx(freq_table,"C:\\Users\\pnuka\\OneDrive\\Documents\\Fall 2022\\Research- Stat\\GitHub\\LogisticFT.xlsx")
#freq_table
```


```{r message=FALSE, warning=FALSE}
require(plotrix)

m_vector <- sapply(train_swag_svml$CVs, function(x) summary(x)[4])

l_vector <- sapply(train_swag_svml$CVs, function(x) summary(x)[1])

u_vector <- sapply(train_swag_svml$CVs, function(x) summary(x)[6])

plotCI(1:length(train_swag_svml$CVs), m_vector, ui=u_vector, li=l_vector, scol = "grey", col="red", pch = 16, main = "Ranges 10-fold CV Misclassification Errors",ylab = "Range CV Error",xlab = "Model Size")
```

The plot shows the range of CV errors for each dimension. There is a clear decay in CV errors as the dimension increases.


\begin{table}
\centering
\begin{tabular}[t]{||c|c|c||}
\hline
Feature & Variable & Frequency \\
\hline \hline
'Insula-R' $\leftrightarrow$ 'Paracentral-Lobule-R' & 54.21 &	381 \\
\hline
'Frontal-Sup-R'$\leftrightarrow$ 'Frontal-Mid-R' & 72.68 & 381 \\
\hline
'Temporal-Mid-L'$\leftrightarrow$ 'Lingual-L'& 101.85 &	381\\
\hline
'Insula-L'$\leftrightarrow$ 'Frontal-Mid-L' & 116.89 & 381\\
\hline
'Frontal-Sup-R'$\leftrightarrow$ 'Frontal-Inf-Orb-R' & 104.34 & 377\\
\hline
'Supp-Motor-Area-L'$\leftrightarrow$ 'SupraMarginal-L' & 151.147 & 377\\
\hline
Frontal-Sup-R'$\leftrightarrow$ 'ParahippocampaGyrus' & 72.11 &	363\\
\hline
'Vermis-1-2'$\leftrightarrow$ 'Temporal-Mid-L' & 150.114 & 363\\
\hline
'Vermis-4-5'$\leftrightarrow$ 'Frontal-Sup-Orb-R' & 126.2	& 325\\
\hline
'Frontal-Sup-Medial-L'$\leftrightarrow$ 'Cingulum-Mid-L'& 124.99 & 284\\
\hline
'Temporal-Mid-L'$\leftrightarrow$ 'Pallidum-R'& 114.40 & 281\\
\hline
'Occipital-Mid-L'$\leftrightarrow$ 'Cerebelum-Crus2-L' & 162.73 & 267\\
\hline
'Cingulum-Ant-L'$\leftrightarrow$ Paracentral-Lobule-R' & 47.21	& 258\\
\hline
'Temporal-Pole-Sup-R'$\leftrightarrow$ 'Frontal-Mid-L' & 146.89 & 235\\
\hline
'Frontal-Mid-L'$\leftrightarrow$ 'Caudate-R' & 108.27 & 207\\
\hline
'Frontal-Mid-L'$\leftrightarrow$ 'Frontal-Sup-L' & 108.91 & 201\\
\hline
'Temporal-Mid-L'$\leftrightarrow$ 'Temporal-Sup-L' & 114.28 & 172\\
\hline
'Frontal-Sup-R'$\leftrightarrow$ 'Precuneus-R' & 173.9 & 149\\
\hline
'Insula-L'$\leftrightarrow$ 'Postcentral-R' & 116.55 & 84\\
\hline
'Frontal-Mid-L'$\leftrightarrow$ 'Cingulum-Ant-L' & 108.47 & 73\\
\hline
'Frontal-Sup-Medial-R'$\leftrightarrow$ 'Cingulum-Mid-L' & 134.99	& 66\\
\hline
'Cingulum-Post-L'$\leftrightarrow$ 'Postcentral-R' & 74.55 & 63\\
\hline
'Supp-Motor-Area-L'$\leftrightarrow$ 'SupraMarginal-L'& 151.46 & 55\\
\hline
'Frontal-Sup-L'$\leftrightarrow$ 'ParahippocampaGyrus' & 13.11 & 51\\
\hline
'Caudate-R'$\leftrightarrow$ 'Paracentral-Lobule-R'& 27.21	& 51\\
\hline
'Frontal-Sup-Medial-R'$\leftrightarrow$ 'Frontal-Inf-Tri-L'& 134.23 & 46\\
\hline
'Insula-L'$\leftrightarrow$ 'Paracentral-Lobule-R'& 116.21 &	45\\
\hline
'Cingulum-Post-L'$\leftrightarrow$ 'Paracentral-Lobule-R'& 74.21 &	43\\
\hline
'Parietal-Sup-R'$\leftrightarrow$ 'Cuneus-L'& 184.58 & 37\\
\hline
'Cingulum-Ant-R'$\leftrightarrow$ 'Frontal-Sup-R'& 189.173 &	37\\
\hline
'Parietal-Inf-L'$\leftrightarrow$ 'Caudate-Head-L'& 169.49 &	34\\
\hline
'Frontal-Sup-Medial-L'$\leftrightarrow$ 'Frontal-Inf-Tri-L'& 124.23 &	28\\
\hline
'Insula-R'$\leftrightarrow$ 'Pallidum-R'& 129.40 & 25\\
\hline
'Temporal-Mid-L'$\leftrightarrow$ 'Putamen-L'& 114.6 & 23\\
\hline
'Insula-L'$\leftrightarrow$ 'Cingulum-Ant-L'& 116.47 & 23\\
\hline
'Caudate-Head-L'$\leftrightarrow$ 'Cingulum-Ant-L'& 49.47 & 21\\
\hline
'Frontal-Med-Or-R'$\leftrightarrow$ 'Frontal-Inf-Tri-L'& 138.23 &	20\\
\hline
'Vermis-4-5'$\leftrightarrow$ 'Frontal-Sup-Medial-L'& 126.124 &	18\\
\hline
'Frontal-Sup-R'$\leftrightarrow$ 'Cingulum-Ant-L'& 173.47 &	13\\
\hline
'Cingulum-Mid-R'$\leftrightarrow$ 'Frontal-Sup-L'& 82.13 &	12\\
\hline
'Frontal-Med-Orb-R'$\leftrightarrow$ 'Frontal-Mid-R'& 138.107 &	9\\
\hline
'Rolandic-Oper-L'$\leftrightarrow$ 'Temporal-Inf-L'& 148.71 &	9\\
\hline
'Lingual-L'$\leftrightarrow$ 'Frontal-Sup-L'& 85.13 &	8\\
\hline
'Cingulum-Ant-R'$\leftrightarrow$ 'Frontal-Mid-L'& 112.67	& 7\\
\hline
'Cingulum-Ant-R'$\leftrightarrow$ 'Cingulum-Mid-L'& 189.65 &	7\\
\hline
'Cingulum-Ant-L'$\leftrightarrow$ 'Precuneu-R'& 47.9 &	5\\
\hline
'Pallidum-R'$\leftrightarrow$ 'Temporal-Mid-R'& 40.19 &	3\\
\hline
'Caudate-Head-L'$\leftrightarrow$ 'Precuneus-R'& 49.9 &	3\\
\hline
'Cingulum-Ant-L'$\leftrightarrow$ 'Caudate-R'& 47.27 &	1\\
\hline
'Temporal-Inf-L'$\leftrightarrow$ 'Lingual-L'& 132.85	& 1\\
\hline
'Temporal-Sup-L'$\leftrightarrow$ 'Temporal-Mid-L'& 135.114 &	1\\
\hline
'Vermis-6'$\leftrightarrow$ 'Temporal-Inf-L'& 136.132 &	1\\
\hline
'Cingulum-Ant-R'$\leftrightarrow$ 'Paracentral-Lobule-R'& 189.21 & 1\\
\hline
\end{tabular}
\end{table}

There are a total of 381 models of dimensions 9 to 20. The table below shows the frequency of each feature selected. The most frequent features are 'Insula_R' \(\leftrightarrow\) 'Paracentral-Lobule-R', 'Frontal-Sup-R' \(\leftrightarrow\) 'Frontal-Mid-R', 'Temporal-Mid-L' \(\leftrightarrow\) 'Lingual-L' and 'Insula-L' \(\leftrightarrow\) 'Frontal-Mid-L',  which are contained by every model.
