---
title: "ADHD-SVM Linear Analysis"
output: pdf_document
date: '2022-11-16'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
```

## LOADING AND ORGANIZING THE DATA

```{r}
DATA <-  read.csv("train_data.csv")
adhd0 <- t(DATA)
adhd1 <- adhd0[-1, ]

#naming the colnames
colnames(adhd1) <- as.character(adhd1[1, ])
X <- apply(adhd1[,-1],2, as.numeric)
X <- data.frame(adhd1[ ,1],X)
adhd2 <- X[-1, ]
adhd3 <- as.matrix(adhd2)
colnames(adhd3)[1] <- "GROUP"

#defining control group=0  
cat_v <- c()
for (i in 1:dim(adhd3)[1]){
  if(adhd3[ ,"GROUP"][i] == "Controls")
  {
    cat_v[i]<-"0"
  }else{
    cat_v[i]<-"1"
  }
}
#as.factor(cat_v)
adhd3 <- data.frame(cat_v, adhd3)
Z <- adhd3[ ,-2]
Z <- apply(Z,2,as.numeric)
r <- Z[ ,1]
r <- as.matrix(r)
adhd <- Z[ ,-1]

rm(list=c("adhd0", "adhd1", "adhd2", "adhd3", "Z"))
```

## TRAINING AND TESTING DATA

```{r}
#training and testing data
## % 80 of the sample size
ind <- floor(0.8 * nrow(adhd))
set.seed(2705)
train_ind <- sample(seq_len(nrow(adhd)), size = ind)

x_train <- as.data.frame(adhd[train_ind, ])
y_train <- as.factor(r[train_ind, ])
x_test <- as.data.frame(adhd[-train_ind, ])
y_test <- as.factor(r[-train_ind, ])
```

## LOADING THE SWAG SVM LINEAR RESULTS


```{r message=FALSE, warning=FALSE}
## Loading the SWAG SVM Linear results
load("SVMLinear_Results.Rda")
```

```{r message=FALSE, warning=FALSE}
## Post-processing
min_error = min(train_swag_svml$cv_alpha)


varmat_ind = list() #saves the varmat index from CV errors
for(i in 1:20){
  varmat_ind[[i]]=which(train_swag_svml$CVs[[i]]<=min_error, arr.ind = T)
}

post_sel = list() # models selected after post-processing
for(i in 1:20){
  post_sel[[i]] = train_swag_svml$VarMat[[i]][,varmat_ind[[i]]]
}

post_sel[[1]] = t(as.matrix(post_sel[[1]]))

for(i in 1:20){
  if(!is.matrix(post_sel[[i]])){
    post_sel[[i]]=t(as.matrix(post_sel[[i]]))
  }
}

post_sel[[9]] = t(post_sel[[9]])


x = c() #non-empty elements of post-group
for(i in 1:20){
  if(length(post_sel[[i]])!=0){
    x = c(x,i)
  }
  x = x
}

for(i in 1:length(x)){
  if(nrow(post_sel[[x[i]]])<20){
    diff = 20 - nrow(post_sel[[x[i]]])
    post_sel[[x[i]]] = rbind(post_sel[[x[i]]],matrix(NA,nrow = diff, ncol = ncol(post_sel[[x[i]]])))
  } 
}


models = matrix(NA, nrow = 20,ncol=ncol(post_sel[[x[1]]]))

models[1:nrow(post_sel[[x[1]]]),]=post_sel[[x[1]]]

for(i in 2:length(x)){
  models = cbind(models,post_sel[[x[i]]])
}

models = t(models)

selected_var = c() 
for(i in 1:ncol(models)){
  selected_var = c(selected_var,models[,i])
}
selected_var = na.omit(unique(selected_var))
selected_var = sort(selected_var)
#colnames(x_train)[selected_var]
#table(models)

freq = table(models)
variable = colnames(x_train)[selected_var]

freq_table = cbind(variable,freq)
rownames(freq_table) = c(1:nrow(freq_table))
freq_table = as.data.frame(freq_table)
freq_table$freq = as.numeric(freq_table$freq)

#freq_table
```


```{r message=FALSE, warning=FALSE}
require(plotrix)

m_vector <- sapply(train_swag_svml$CVs, function(x) summary(x)[4])

l_vector <- sapply(train_swag_svml$CVs, function(x) summary(x)[1])

u_vector <- sapply(train_swag_svml$CVs, function(x) summary(x)[6])

plotCI(1:length(train_swag_svml$CVs), m_vector, ui=u_vector, li=l_vector, scol = "grey", col="red", pch = 16, main = "Ranges 10-fold CV Misclassification Errors",ylab = "Range CV Error",xlab = "Model Size")
```

The plot shows the range of CV errors for each dimension.

## FREQUENCY TABLE

In the post-processing, we took the minimum CV_alpha and selected all the models who have CV_alpha less than or equal to it. The minimum CV_alpha is 0.220925 and is the CV of dimension 20.

There are a total of 114 models of dimensions 18, 19, 20. "54,21", "91,85", "105,10", "121,68", "126,2", "135,105", "140,53", "150,114", "152,22", "154,112", "174,73" features are present in all the models. Below is the frequency table.

\begin{table}
\begin{tabular}[t]{||c|c|c||}
\hline
Feature & Variable & Frequency \\
\hline \hline
'Insula-R'$\leftrightarrow$ 'Paracentral-Lobule-R'& 54.21 &	114 \\
\hline
'Frontal-Sup-L'$\leftrightarrow$ 'Lingual-L' & 91.85 & 114 \\
\hline
'Thalamus-L'$\leftrightarrow$ 'Frontal-Sup-Medial-L' & 105.10 & 114\\
\hline
'Olfactory'$\leftrightarrow$ 'Frontal-Mid-R' & 121.68 &	114\\
\hline
'Vermis-4-5'$\leftrightarrow$ 'Frontal-Sup-Orb-R' & 126.2 &	114\\
\hline
'Temporal-Sup-L'$\leftrightarrow$ 'Thalamus-L' & 135.105 &	114\\
\hline
'Parietal-Inf-R'$\leftrightarrow$ 'Precentral-R' & 140.53 &	114\\
\hline
'Vermis-1-2'$\leftrightarrow$ 'Temporal-Mid-L'& 150.114	& 114\\
\hline
'Angular-R'$\leftrightarrow$ 'Fusiform-L'& 152.22 & 114\\
\hline
'Fusiform-R'$\leftrightarrow$ 'Cingulum-Ant-R' & 154.112	& 114\\
\hline
'Cerebelum-6-L'$\leftrightarrow$ 'Cerebelum-Crus2-L' & 174.73	& 114\\
\hline
'Parietal-Inf-L'$\leftrightarrow$ 'Temporal-Pole-Mid-L'& 183.12	& 106\\
\hline
'Thalamus-L'$\leftrightarrow$'Frontal-Sup-L' & 105.91	& 71\\
\hline
'Vermis-1-2'$\leftrightarrow$'Pallidum-R' & 150.40	& 67\\
\hline
'Cuneus-R'$\leftrightarrow$'Frontal-Inf-Orb-L' & 70.14	& 66\\
\hline
'Frontal-Sup-Medial-L'$\leftrightarrow$'Precentral-L' & 130.80	& 66\\
\hline
'Frontal-Mid-R'$\leftrightarrow$'Cingulum-Ant-L' & 161.47 & 66\\
\hline
'Parietal-Inf-L'$\leftrightarrow$'Fusiform-R' & 157.81	& 56\\
\hline
'Frontal-Sup-Orb-L'$\leftrightarrow$'Cuneus-L' & 78.58	& 40\\
\hline
'Angular-R'$\leftrightarrow$'Cerebelum-Crus2-L' & 92.73	& 39\\
\hline
'Rolandic-Oper-L'$\leftrightarrow$'Frontal-Inf-Orb-L' & 148.14	& 28\\
\hline
'Midbrain'$\leftrightarrow$'Temporal-Sup-L' & 165.135 & 27\\
\hline
'Temporal-Pole-Sup-R'$\leftrightarrow$'Frontal-Inf-Orb-R' & 185.34	& 24\\
\hline
'Cingulum-Ant-R'$\leftrightarrow$'Temporal-Mid-R' & 189.8	& 22\\
\hline
'SupraMarginal-L'$\leftrightarrow$'Cingulum-Mid-L' & 147.65	& 16\\
\hline
'Parietal-Inf-L'$\leftrightarrow$'Cingulum-Ant-L' & 169.47 & 15\\
\hline
'Frontal-Sup-R'$\leftrightarrow$'Putamen-L' & 72.6 & 12\\
\hline
'Precentral-L'$\leftrightarrow$'Occipital-Mid-R'& 80.77 & 12\\
\hline
'Temporal-Mid-L'$\leftrightarrow$'Frontal-Inf-Orb-L' & 187.14 & 11\\
\hline
'Parietal-Inf-L'$\leftrightarrow$'Precuneus-L' & 169.18 & 10\\
\hline
'Frontal-Inf-Oper-R'$\leftrightarrow$'SupraMarginal-R' & 190.127 & 10\\
\hline
'Occipital-Mid-R'$\leftrightarrow$'Lingual-R' & 77.4 & 9\\
\hline
'Occipital-Sup-R'$\leftrightarrow$'Parietal-Sup-R' & 137.131 &	9\\
\hline
'Thalamus-R'$\leftrightarrow$'Frontal-Sup-Medial-L' & 62.10 & 8\\
\hline
'Temporal-Mid-L'$\leftrightarrow$'Frontal-Mid-R & 114.68 & 8\\
\hline
'Frontal-Mid-L'$\leftrightarrow$'Frontal-Sup-L' & 79.13 & 7\\
\hline
'Cingulum-Ant-R'$\leftrightarrow$'Frontal-Inf-Orb-R' & 189.34 & 7\\
\hline
'Insula-L'$\leftrightarrow$'Brainstem' & 61.35 &	6\\
\hline
'Calcarine-L'$\leftrightarrow$'Cerebelum-8-R' & 88.45 &	6\\
\hline
'Frontal-Med-Orb-R'$\leftrightarrow$'Frontal-Mid-L'& 138.89 & 6\\
\hline
'Rolandic-Oper-L'$\leftrightarrow$'Temporal-Pole-Sup-R'& 148.146 & 6\\
\hline
'Frontal-Inf-Orb-L'$\leftrightarrow$'Putamen-L'& 14.6 & 5\\
\hline
'Cingulum-Mid-R'$\leftrightarrow$'Frontal-Mid-L' & 82.69	& 5\\
\hline
'Temporal-Pole-Sup-R'$\leftrightarrow$'Supp-Motor-Area-R' & 146.30 &	5\\
\hline
'Cerebelum-8-R'$\leftrightarrow$'Cerebelum-6-L' & 155.7 & 5\\
\hline
'Rectus-L'$\leftrightarrow$'Brainstem' & 188.35 & 5\\
\hline
'Rectus-L'$\leftrightarrow$'Cingulum-Mid-L' & 188.99 & 5\\
\hline
'Rectus-L'$\leftrightarrow$'Cerebelum-6-L' & 188.174 & 5\\
\hline
'Cingulum-Ant-R'$\leftrightarrow$'Temporal-Mid-R' & 189.64 & 5\\
\hline
'Frontal-Inf-Oper-R'$\leftrightarrow$'Frontal-Inf-Tri-R' & 190.3 &	5\\
\hline
'Cuneus-L'$\leftrightarrow$'Precuneus-L' & 58.38 & 4\\
\hline
'Thalamus-L'$\leftrightarrow$'Frontal-Sup-Medial-R' & 105.83 & 4\\
\hline
'Frontal-Mid-L'$\leftrightarrow$'Frontal-Sup-Medial-L' & 108.10 & 4\\
\hline
'Occipital-Sup-R'$\leftrightarrow$'Precuneus-R' & 137.9 &	4\\
\hline
'Frontal-Inf-Oper-R'$\leftrightarrow$'Cingulum-Mid-R' & 164.82 & 4\\
\hline
'Midbrain'$\leftrightarrow$'Frontal-Inf-Tri-L' & 165.23 & 4\\
\hline
'Cerebelum-6-L'$\leftrightarrow$'Temporal-Inf-R' & 174.57 & 4\\
\hline
'Frontal-Sup-R'$\leftrightarrow$'Frontal-Mid-Orb-R'& 104.90 & 3\\
\hline
'Insula-L'$\leftrightarrow$'Supp-Motor-Area-R' & 116.30 & 3\\
\hline
'Insula-L'$\leftrightarrow$'Postcentral-R' & 116.42 & 3\\
\hline
'Caudate-R'$\leftrightarrow$'Temporal-Pole-Mid-R' & 117.102 & 3\\
\hline
'Precentral-L'$\leftrightarrow$'Insula-L' & 128.116 & 3\\
\hline
'Temporal-Sup-L'$\leftrightarrow$'Cingulum-Mid-R' & 135.82 & 3\\
\hline
'Supp-Motor-Area-L'$\leftrightarrow$'Angular-L' & 139.118 & 3\\
\hline
'Precuneus-L'$\leftrightarrow$'Precuneus-L' & 145.18 &	3\\
\hline
'RectalGyrus'$\leftrightarrow$'Frontal-Inf-Orb-R' & 168.34 & 3\\
\hline
'Cuneus-L'$\leftrightarrow$'Cingulum-Ant-L' & 58.47 &	2\\
\hline
'Occipital-Mid-R'$\leftrightarrow$'Temporal-Mid-R' & 77.19 &	2\\
\hline
'Frontal-Sup-Medial-R'$\leftrightarrow$'Caudate-R' & 83.27 & 2\\
\hline
'Angular-R'$\leftrightarrow$'Frontal-Sup-Orb-R' & 92.2 & 2\\
\hline
'Supp-Motor-Area-L'$\leftrightarrow$'SupraMarginal-L' & 151.147	& 2\\
\hline
'RectalGyrus'$\leftrightarrow$'Cerebelum-8-R' & 168.97 & 2\\
\hline
'Paracentral-Lobule-L'$\leftrightarrow$'Postcentral-R' & 177.55 & 2\\
\hline
'Paracentral-Lobule-L'$\leftrightarrow$'Cingulum-Mid-L' & 177.65 & 2\\
\hline
'Temporal-Mid-L'$\leftrightarrow$'Cingulum-Ant-L' & 179.47 & 2\\
\hline
'Parietal-Inf-L'$\leftrightarrow$'Angular-L' & 183.118 & 2\\
\hline
'Cingulum-Ant-R'$\leftrightarrow$'Cingulum-Mid-L' & 189.99 & 2\\
\hline
'Cuneus-L'$\leftrightarrow$Putamen-L' & 24.6 & 1\\
\hline
'Insula_L'$\leftrightarrow$'Temporal_Mid_L' & 61.31 &	1\\
\hline
'Frontal-Mid-L'$\leftrightarrow$'Temporal-Inf-R'& 69.15 & 1\\
\hline
'Cingulum-Mid-R'$\leftrightarrow$'Precentral-L' & 82.80 & 1\\
\hline
'Parietal-Sup-L'$\leftrightarrow$'Precentral-R' & 95.53 &	1\\
\hline
'Cingulum-Mid-L'$\leftrightarrow$'Frontal-Inf-Orb-L' & 99.14 & 1\\
\hline
'Temporal-Inf-L'$\leftrightarrow$'Frontal-Sup-L' & 103.91 & 1\\
\hline
'Frontal-Sup-R'$\leftrightarrow$'Paracentral-Lobule-R'& 104.21 & 1\\
\hline
'Vermis-9'$\leftrightarrow$'Frontal-Mid-R' & 113.107 & 1\\
\hline
'Temporal-Mid-L'$\leftrightarrow$'Frontal-Sup-R' & 114.72 &	1\\
\hline
'Postcentral-R'$\leftrightarrow$'Insula-R' & 115.54 & 1\\
\hline
'Insula-L'$\leftrightarrow$'Parietal-Sup-L' & 116.95 & 1\\
\hline
'Frontal-Mid-Orb-L'$\leftrightarrow$'Cingulum-Mid-L' & 119.99 & 1\\
\hline
'Frontal-Sup-Medial-L'$\leftrightarrow$'Frontal-Inf-Orb-R' & 124.34 & 1\\
\hline
'Temporal-Sup-L'$\leftrightarrow$'Postcentral-R' & 135.55 & 1\\
\hline
'Frontal-Med-Orb-R'$\leftrightarrow$'Angular-R' & 138.92 & 1\\
\hline
'Supp-Motor-Area-L'$\leftrightarrow$'Frontal-Mid-R'& 139.20 & 1\\
\hline
'Temporal-Pole-Sup-R'$\leftrightarrow$'Temporal-Mid-L' & 146.31 & 1\\
\hline
'Temporal-Pole-Sup-R'$\leftrightarrow$'Frontal-Sup-Orb-L' & 146.78 &	1\\
\hline
'SupraMarginal-L'$\leftrightarrow$'Frontal-Mid-Orb-L' & 147.33 & 1\\
\hline
'Rolandic-Oper-L'$\leftrightarrow$'Cingulum-Ant-L' & 148.47 & 1\\
\hline
'Rolandic-Oper-L'$\leftrightarrow$'Frontal-Mid-L' &148.89 & 1\\
\hline
'Cerebelum-3-R'$\leftrightarrow$'Thalamus-R' & 160.62 & 1\\
\hline
'Postcentral-L'$\leftrightarrow$'Postcentral-R' & 163.55 & 1\\
\hline
'Precentral-L'$\leftrightarrow$'Cingulum-Ant-R' & 166.112 & 1\\
\hline
'RectalGyrus'$\leftrightarrow$'Insula-L' & 168.116 &	1\\
\hline
'Parietal-Inf-L'$\leftrightarrow$'Frontal-Mid-L' & 169.108	& 1\\
\hline
'Occipital-Sup-L'$\leftrightarrow$'Occipital-Mid-R' & 171.59 & 1\\
\hline
'Frontal-Inf-Orb-R'$\leftrightarrow$'Vermis-6' & 172.136 & 1\\
\hline
'Fusiform-R'$\leftrightarrow$'Caudate-R' & 175.27 & 1\\
\hline
'Parietal-Inf-L'$\leftrightarrow$'Paracentral-Lobule-R' & 183.21 & 1\\
\hline
'Temporal-Pole-Sup-R'$\leftrightarrow$'Thalamus-R' & 185.62 &	1\\
\hline
'Temporal-Mid-L'$\leftrightarrow$'Temporal-Inf-L' & 187.60 &	1\\
\hline
\end{tabular}
\end{table}




